Guided Proofreading of Automatic Segmentations for Connectomics

### 2017-03-17 paper/results.tex
Fix section 5.1.

\subsection{Precision and Recall}

\paragraph{L.~Cylinder.} Evaluation was performed on previously unseen sections of the mouse cortex volume from Kasthuri~\etal~\cite{kasthuri2015saturated}. We generated an unbalanced dataset of 81,184 correct and 8,780 split error patches with respect to the ground truth labeling. Then, we ranked each patch by using focused proofreading and guided proofreading, and compare precision/recall (Fig. \ref{fig:pr}). Our method exhibits higher precision and recall.% for correct and erroneous patches.

@@

\paragraph{AC4 subvolume.} We generated 3,488 correct and 332 error patches (10 merge errors, 322 split errors). Guided proofreading achieves better precision/recall scores (Fig. \ref{fig:pr}).

>>>>

\subsection{Classification Performance}

\paragraph{L.~Cylinder.} Evaluation was performed on previously unseen sections of the mouse cortex volume from Kasthuri~\etal~\cite{kasthuri2015saturated}. We generated an unbalanced dataset of 81,184 correct and 8,780 split error patches with respect to the ground truth labeling. Then, we ranked each patch by using focused proofreading and guided proofreading, and compare classification performance (Fig. \ref{fig:pr}). Our method exhibits higher sensitivity.% for correct and erroneous patches.

@@

\paragraph{AC4 subvolume.} We generated 3,488 correct and 332 error patches (10 merge errors, 322 split errors). Guided proofreading achieves better classification performance (Fig. \ref{fig:pr}).
